\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/paper.tex

>>>>

\FigIpBits

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as dark decoys. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright. For a specific deployment,
operators should be careful to observe the distribution of addresses in the subnets they use,
and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).
